% =============================================================
%  Chapter — Standards & Standardization Bodies
%  Key players in the standardization and publication landscape
%  relevant to HVDC: IEC, IEEE, CIGRE.
% =============================================================
\sectionslide{Standardization Bodies}{Who writes the standards and technical recommendations}

% ---- IEC ----------------------------------------------------
\begin{frame}{IEC\\International Electrotechnical Commission}
  \begin{block}{Role}
    The world's leading organization for international standards in electrical, electronic and related technologies.
  \end{block}
  \vspace{0.3em}
  \begin{itemize}
    \setlength{\itemsep}{0.4em}
    \item Founded 1906; headquartered in Geneva, Switzerland.
    \item Consensus-based, normative standards developed by national committees and technical committees (e.g. TC~115 for HVDC).
    \item Also runs conformity-assessment / certification schemes.
    \item IEC standards are noramative for countries adopting the IEC standards
  \end{itemize}
\end{frame}


% ---- IEEE ---------------------------------------------------
\begin{frame}{IEEE\\Institute of Electrical and Electronics Engineers}
  \begin{block}{Role}
    The world's largest technical professional organization; publisher of
    standards, journals and conference proceedings.
  \end{block}
  \vspace{0.3em}
  \begin{itemize}
    \setlength{\itemsep}{0.4em}
    \item Standards developed through the IEEE Standards Association (IEEE~SA).
    \item Especially influential in North American practice
    \item Power \& Energy Society (PES) covers transmission, HVDC and FACTS.
    \item IEEE standards are not normative, unless adopted by individual network operators
  \end{itemize}
\end{frame}


% ---- CIGRE --------------------------------------------------
\begin{frame}{CIGRE\\International Council on Large Electric Systems}
  \begin{block}{Role}
    A global collaborative community pooling operator, manufacturer and
    academic expertise on large electric power systems.
  \end{block}
  \vspace{0.3em}
  \begin{itemize}
    \setlength{\itemsep}{0.4em}
    \item Founded 1921; headquartered in Paris, France.
    \item Output: \textbf{Technical Brochures} (TBs) and conference publications
    \item Work organized into \textbf{16 Study Committees} across four domains (HVDC sits in \textbf{SC~B4}).
    \item CIGRE Technical Brochures are authoritative guidance and state-of-the-art references.
    \item TBs frequently become the technical basis for later IEC/IEEE standards.
  \end{itemize}
\end{frame}


\begin{frame}{CIGRE\\Study Committees}
  {\color{atGray}\small 16 Study Committees grouped into four domains:}
  \vspace{0.6em}
  \begin{columns}[T,onlytextwidth]
    \begin{column}{0.48\textwidth}
      {\color{atAccent}\textbf{A — Equipment}}\\[0.35em]
      \footnotesize
      \textbf{A1} Rotating Electrical Machines\\[0.25em]
      \textbf{A2} Power Transformers \& Reactors\\[0.25em]
      \textbf{A3} Transmission \& Distribution Equipment
    \end{column}
    \begin{column}{0.48\textwidth}
      {\color{atAccent}\textbf{B — Subsystems}}\\[0.35em]
      \footnotesize
      \textbf{B1} Insulated Cables\\[0.25em]
      \textbf{B2} Overhead Lines\\[0.25em]
      \textbf{B3} Substations \& Electrical Installations\\[0.25em]
      {\color{atInk}\textbf{B4} DC Systems \& Power Electronics}\\[0.25em]
      \textbf{B5} Protection \& Automation
    \end{column}
  \end{columns}
  \vspace{0.8em}
\end{frame}


\begin{frame}{CIGRE\\Study Committees}
  {\color{atGray}\small 16 Study Committees grouped into four domains:}
  \vspace{0.6em}
  \begin{columns}[T,onlytextwidth]
    \begin{column}{0.48\textwidth}
      {\color{atAccent}\textbf{C — System}}\\[0.35em]
      \footnotesize
      \textbf{C1} System Development \& Economics\\[0.25em]
      \textbf{C2} System Operation \& Control\\[0.25em]
      \textbf{C3} System Environmental Performance\\[0.25em]
      \textbf{C4} System Technical Performance\\[0.25em]
      \textbf{C5} Electricity Markets \& Regulation\\[0.25em]
      \textbf{C6} Active Distribution \& DER
    \end{column}
    \begin{column}{0.48\textwidth}
      {\color{atAccent}\textbf{D — Materials}}\\[0.35em]
      \footnotesize
      \textbf{D1} Materials \& Emerging Test Techniques\\[0.25em]
      \textbf{D2} Information Systems \& Telecommunication
    \end{column}
  \end{columns}
  \vspace{0.8em}
\end{frame}


% ---- EPRI ---------------------------------------------------
\begin{frame}{EPRI\\Electric Power Research Institute}
  \begin{block}{Role}
    Independent, non-profit R\&D organization serving the electric power
    industry — research, not standards.
  \end{block}
  \vspace{0.3em}
  \begin{itemize}
    \setlength{\itemsep}{0.4em}
    \item Founded 1972; headquartered in Palo Alto, California.
    \item Funded by and for the industry; collaborates with 450+ companies across ~45 countries.
    \item Covers generation, delivery and end-use of electricity — reliability, efficiency, safety and environment.
    \item Output: research reports, technical guidelines and testing that inform utility practice.
  \end{itemize}
\end{frame}


% ---- ESIG ---------------------------------------------------
\begin{frame}{ESIG\\Energy Systems Integration Group}
  \begin{block}{Role}
    Non-profit technical \& educational association focused on integrating
    new resources and technologies into the power system.
  \end{block}
  \vspace{0.3em}
  \begin{itemize}
    \setlength{\itemsep}{0.4em}
    \item Formerly UVIG (Utility Variable-Generation Integration Group); renamed in 2018 after merging with iiESI.
    \item Focus: high levels of renewables / inverter-based resources, HVDC and emerging technologies on the grid.
    \item Members: utilities, operators, manufacturers, labs, universities and consultants.
    \item Output: reports, workshops, webinars and short courses — guidance and best practice, not normative.
  \end{itemize}
\end{frame}

